\documentclass[x11names,dvipsnames,svgnames,table,xcdraw]{mmuthesis}
%\newsubfloat{figure}

\usepackage{lipsum}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{enumerate}
\usepackage{float}
\usepackage[noend]{algcompatible}

% for the degree symbol
\usepackage{siunitx}

% landscape
\usepackage{lscape}

\usepackage[x11names,dvipsnames,svgnames]{xcolor}
\usepackage[os=win]{menukeys}
\usepackage{listings}
\usepackage{xspace}


% -------------------------------------------------------------------
% own package
% \usepackage[table,xcdraw]{xcolor}
% -------------------------------------------------------------------

\lstset{language=[LaTeX]TeX,columns=fullflexible,
basicstyle=\ttfamily,texcsstyle=*\bfseries\color{NavyBlue},
commentstyle=\itshape\color{PaleVioletRed4},
frame=single,framesep=6pt,
framexleftmargin=6pt,framexrightmargin=6pt,
xleftmargin=12pt,xrightmargin=12pt,
breaklines=true,breakatwhitespace=true}


% -------------------------------------------------------------------
% user annotations
% -------------------------------------------------------------------

% \begin{comment}
\newcommand{\ian}[1]{\textcolor{red}{#1}}
\newcommand{\lk}[1]{\textcolor{blue}{#1}}
\newcommand{\js}[1]{\textcolor{magenta}{#1}}
\newcommand{\cc}[1]{\textcolor{teal}{#1}}
\newcommand{\rl}[1]{\textcolor{green}{#1}}
% \end{comment}

\begin{comment}
\newcommand{\ian}[1]{}   % turn off
\newcommand{\lk}[1]{}   % turn off
\newcommand{\js}[1]{}   % turn off
\newcommand{\cc}[1]{}   % turn off
\newcommand{\rl}[1]{}   % turn off
\end{comment}


\newcommand*\mean[1]{\bar{#1}}
\newcommand{\versionOneExt}{{Phase 1: LSH-Inspired Semantic Extraction}\xspace}
\newcommand{\versionTwoExt}{{Phase 2: Chamfer Distance-Inspired Semantic Extraction}\xspace}

\newcommand{\versionOneRet}{{Phase 1: LSH-Inspired Retrieval Technique}\xspace}
\newcommand{\versionTwoRet}{{Phase 2: Chamfer Distance based Retrieval Technique}\xspace}




% -------------------------------------------------------------------
% own packages
% -------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{multirow}

%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}
%%% END HELPER CODE

% % put all the external documents here!
% % \myexternaldocument{File2}
% \myexternaldocument{1introduction}
% \myexternaldocument{2literature-review}
% \myexternaldocument{3framework-overview}
% \myexternaldocument{4vehicle-semantics-extraction}
% \myexternaldocument{5retrieval-module}
% \myexternaldocument{6conclusion}




\author{Clarence Cheong Weihan}
\title{Extraction and Retrieval of Vehicle Semantics for Long-Term Car Park Videos}
\submissionyear{2021}
\submissionmonth{March}
\faculty{Faculty of Computing and Informatics}
\degree{Master~of~Science (Information~Technology)}
\qualification{B.Eng.~(Hons), Multimedia University, Malaysia\\%
}

% load acronym definitions from separate file
\loadglsentries{myacronyms}

\begin{document}

\frontmatter
\makecoverandtitlepage
\copyrightpage
\declarationpage

\acknowledgements{
Firstly, I would like to thank my wife, Jocelyn for encouraging me to take on
this seemingly "less travelled road". Her unceasing support and understanding
throughout this journey is precious and much appreciated.

Undeniably, this journey would not be possible without the advises,
ideas and guidance provided by my supervisors, Dr. John See as well as
Dr. Wong Lai Kuan. Their input certainly has sparked ideas which has been
materialised in this work. Thank you, I owe you many.

To my sponsor who supported my studies, thank you for this timely opportunity to
explore this vast ocean of computer vision and its applications. My Masters
journey has been one full of excitement. I'm thankful for the opportunity to
attend and publish multiple conference papers and even the chance to attend my
first Hackathon in 2017. Not forgetting, obtaining my first copyright during
this period as well.

Not forgetting my family and friends who supported me on this journey.
My fellow church members who were encouraging me throughout my Masters.
Thanks a lot! Last and not least, I would like to applaud myself and give
myself some credit for putting myself out there, not being afraid to chase
after goals and desires, and to take on challenges that I would have never
thought of.

Thank you everyone! Much blessings.

}
\dedication{To my parents \& family, my wife, and to my son Ralph.}

\abstractfromfile{abstract}

{\clearpage\SingleSpacing
\tableofcontents\clearpage
\listoftables\clearpage
\listoffigures\clearpage}
% \printglossary[type=\acronymtype,title={Abbreviations}]
% \prefacefromfile{preface}

\mainmatter


\include{1introduction}
\include{2literature-review}
\include{3framework-overview}
\include{4vehicle-semantics-extraction}
\include{5retrieval-module}
\include{6conclusion}

% \appendix
% \include{sample-appen-manual}
% \include{sample-appen-try}

\backmatter
\bibliography{llt}
\printglossaries
% \theendnotes
{\SingleSpacing\printindex}

\ownpubs
\nociteconf{cheong2018vehicle,lim2017,cheong2019efficient}
%\nocitejour{Lim:Ranaivo:Tang:Polibits:2011,Lim:Ranaivo:Tang:Procedia:2011}
%\bibliographyjour{llt}
\bibliographyconf{llt}

\end{document}
